---
title: "CMTH_136_Stock_Prediction_Project_v2"
author: "Edward Pickering"
date: "March 19, 2019"
output: html_document
---

## PREPARATION ##

```{r}
#Load packages 
library("quantmod")
library("TTR")
library("ggplot2")
library("MASS")
library("mlbench")
library("caret")
library("rpart")
library("tidyr")
library("FSelectorRcpp")
library("doMC")
library("glmnet")
library("Boruta")
library("FSelector")
library("magrittr")
```

## DATA COLLECTION ##

The sudy period is going to be the 5 year period from January 1, 2014 to March 30, 2019.  Extra data is collected and will be removed after data exploration and cleaning have been performed. 
```{r}
# Download SP500 Index Data
getSymbols("^GSPC", src = "yahoo",
           from = as.Date("2010-01-01"), to = as.Date("2019-03-29"))
```
SP500 is one of the best regarded stock indexes in the world and thus we would expect there to be complete data for the specified period

```{r}
# Check for missing data
sum(is.na(GSPC))
# 0 missing data.  Data for the project is secured. 
```

## DATA EXPLORATION
```{r}
# Count total number of rows
nrow(GSPC)
##  2324 total rows of data
```


```{r}
# Display head and tail of data
head(GSPC)
tail(GSPC)
#Rename column headings
colnames(GSPC) <- c("Open", "High", "Low", "Close", "Volume", "Adjusted" )
```


```{r}
# Look at the class of data
class(GSPC)
```

We can see that GSPC is a xts zoo object in R.  XTS is an object that allows for the storage of time-series data in R by indexing the time/date column. It is an extension to the S3 class from the zoo package hence the class showing as "xts" and "zoo".

```{r}
# Look at the structure and dimensions of the data
str(GSPC)
dim(GSPC)

# Look at summary statistics for the data
summary(GSPC)
```

## NOTES/DISCUSSION ##
When one start to research stock market prediction.  One quickly learns that is is a field that gets so much attention that they already have accepted ways of managing and analysing data, namely with Auto Regression(AR) and Moving Average (MA) or AutoRegressive Moving Average (ARMA) and AutoRegressive Integrated Moving Average (ARIMA)  models.  The object of this project is to predict the stock market.  Therefore after running into some issues with analysis it was decided to start by running an ARIMA model to help learn some of the theory and give a base-line for the prediction model that will come later something to compare to. 

## ARIMA ##

"It is common in financial literature to use the closing price only when working with discrete-time fixed frequency data.  This holds for indicators, rule sets and performance metrics" (Conlan, 2016). In fact Yahoo Finance includes the Adjusted Close price (GSPC.Adjusted) of an asset that takes account of stock splits or dividends.  For ARIMA we need to the log of the Adjusted close price. This is because stocks price are based on returns and returns are based on percentages so using the log will capture that attribute. 

```{r}
#Create xts object that only contains date and Adjusted Price
AP <- GSPC$Adjusted
head(AP)
plot(AP)
```

```{r}
#Create xts object that contains date and logarithmic Adjusted Price
LogAP <- log(AP)
head(LogAP)
plot(LogAP)
```

Split the data into training and test sets
```{r}
#Select the first 80% of the data
dim(LogAP)
LogAP.end <- floor(0.8*length(LogAP)) 

#assign the first 80% of the data to the train set
LogAP.train <- LogAP[1:LogAP.end,] 
nrow(LogAP.train)
#assign the most recent 20% to the test set
LogAP.test <- LogAP[(LogAP.end+1):length(LogAP),] 
nrow(LogAP.test)
```

# Stationarity
Stationarity is a an assumption underlying many statistical procedures used in Time series analysis.  It means that mean and variance and standard deviation should be constant over time.  It is important for time series analysis becaus if the data cannot be see to have a constant mean, variance and standard deviation then there would be little confidence in making forecasts or predictions, rather the Efficient Market Hypothesis and the random walk theory that the stock market cannot be outperformed or predicted with any degree of accuracy.  

When we look at the plots produced above we can see that the SP500 data does not appear to be stationary as the general tread looks to be going up.  There are a number of ways to test for stationarity.  The first is to perform autocorrelation and partial autocorrelation and look at the plots.
```{r}
#Perform autocorrelation
acf(LogAP.train, lag.max = 100)
pacf(LogAP.train, lag.max = 100)
```
With the autocorrelation we see that that there is a gradual consistent decrease in correlation as the lag time increases. The partial autocorrelation shows a large drop in correlation from time 0 to time 1 and none of the remaining correlations show are above or below the dotted blue significance line.  This suggests that the time-series is stationary and has a constant mean, variance and standard deviation, and that there hasn't been a shock to the time series that has had a lasting effect.   

Stationarity can be tested for empirically by the Augmented Dickey-Fuller Test.
```{r}
library("tseries")
#Run Agumented Dickey Fuller Test
adf.test(LogAP.train)
```

The Augmented Dickey-Fuller test has is -2.9554 which is less negative than the tabulated critical values for a sample of greater than 500 at the 95% confidence interval of -3.41 with trend but more than -2.86 without trend.  We cannot reject the null hypothesis of non-stationaity.  To confirm stationarity we can take the differenced time series and run the Augmented Dickey-Fuller test again.

```{r}
#Difference the data.
diffAP.train <- diff(LogAP.train, na.pad = F)

# Run Augmented Dickey-Fuller Test again
adf.test(diffAP.train)
```

Now the Augmented Dickey-Fuller statistic is -12.304 which is more negative than either of the comparison statistics and therefore the null hypothesis of non-stationarity can be rejected. 

Therefore we are now good to run the Autoregression model.  To speed the process an autoregression an auto ARIMA call is going to be made so that the author does not manually have to choose the number of autoregressors, the order of the moving average model and the number of differences.  Auto ARIMA will vary the inputs given to each of the attributes in the model and choose the best one. 

```{r}
library("forecast")
AP.arima <- ts(LogAP.train, start = c(2010, 01), frequency = 252)
class(AP.arima)
head(AP.arima)
fit.AP <- auto.arima(AP.arima)
plot(AP.arima,   type = "l",
     xlab = "Date",
     ylab = "Closing Value",
     main = "S&P 500 Adjusted Closing Price"
     )
exp(LogAP.train)
```



#Arima Forecasted Values
```{r}
nrow(LogAP.test)
#465
forecastAP <- forecast(fit.AP, h = 465)
plot(forecastAP)
head(forecastAP)
```
The final model selected by auto ARIMA is (0, 1, 1) with drift. 


```{r}
#Extract Arima Forecast Values
AP.forecast.extracted <- as.numeric(forecastAP$mean)
AP.final.forecast.values <- exp(AP.forecast.extracted)
AP.final.forecast.values
```

Now we need to test the forecast against the actual recorded prices in the test set. 
```{r}
df <- data.frame(exp(LogAP.test), AP.final.forecast.values)
head(df)
percent_error <- ((df$Adjusted - df$AP.final.forecast.values) / (df$Adjusted))
mean(percent_error)
```
Shows an average of approximately 1% deviation on average between the forecasted and actual prices. 

We now need to test if the the residuals of the autocorrelations are different from Zero and will use the Ljung-box test to do so.  First we will look at the plot of the residuals in a histogram. 

```{r}
hist(fit.AP$residuals)
```
The histogram suggests that the residuals may not be normal — the left tail seems a little too long.


```{r}
Box.test(fit.AP$residuals, lag=1, type = "Ljung-Box")
Box.test(fit.AP$residuals, lag=5, type = "Ljung-Box")
Box.test(fit.AP$residuals, lag=10, type = "Ljung-Box")
```
Not all the p-values are above 0.05, thus we cannot reject the null hypothesis that the residuals are correlated. Therefore, forecasts from this method will probably be quite good, but predictions that are based on a normal distribution may be innacurate. 



## DATA EXPLORATION CONTINUED ##

"Although the actual price movement may also be useful, it is in many cases helpful to look at logarithmic prices.  Exponential development - which is the result of cumulated growth over time - is translated into a linear trend of the logarithmic prices and shows as a straight line trend when you graph the logarithmic prices". (Feuct, 2018).  "Most traders and charting programs us the logarithmic scale" (Investopedia, 2018) and therefore this work will also use the logarithmic values. 

For plotting the data it will be easier if it is transformed into a data.frame

```{r}
# save the data in a data.frame format
sp500.df <- data.frame(
  index(GSPC),
  coredata(GSPC),
  stringsAsFactors=FALSE
)
```

```{r}
# display head of new data frame
head(sp500.df)
colnames(sp500.df) <- c("Date", "Open", "High", "Low", "Close", "Volume", "Adjusted" )
```

For viewing the plots it is useful to have the logarithmic scale overlaid with the actual prices.
```{r}
# Plot the Open prices on a logarithmic scale
plot(x = sp500.df$Date,
     y = sp500.df$Open,
     type = "l",
     xlab = "Date",
     ylab = "Opening Value",
     log = "y",
     main = "S&P 500 Opening Values Since 2010(Logarithmic Scale)"
)
```


```{r}
#Plot Open price density overlaid with the normal distribution
ggplot(sp500.df, aes(x=sp500.df$Open)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "pink") + stat_function(fun = dnorm, lwd = 2, col = 'blue', args = list(mean = mean(sp500.df$Open), sd = sd(sp500.df$Open)))
```

```{r}
# Plot the High prices on a logarithmic scale
plot(x = sp500.df$Date,
     y = sp500.df$High,
     type = "l",
     xlab = "Date",
     ylab = "High Value",
     log = "y",
     main = "S&P 500 High Values Since 2010(Logarithmic Scale)"
)
```
```{r}
#Plot High price density overlaid with the normal distribution
ggplot(sp500.df, aes(x=sp500.df$High)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "pink") + stat_function(fun = dnorm, lwd = 2, col = 'blue', args = list(mean = mean(sp500.df$High), sd = sd(sp500.df$High)))
```


```{r}
# Plot the Low prices on a logarithmic scale
plot(x = sp500.df$Date,
     y = sp500.df$Low,
     type = "l",
     xlab = "Date",
     ylab = "Low Value",
     log = "y",
     main = "S&P 500 Low Values Since 2010(Logarithmic Scale)"
)
```
```{r}
#Plot Low price density overlaid with the normal distribution
ggplot(sp500.df, aes(x=sp500.df$Low)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "pink") + stat_function(fun = dnorm, lwd = 2, col = 'blue', args = list(mean = mean(sp500.df$Low), sd = sd(sp500.df$Low)))
```

```{r}
# Plot the Close prices on a logarithmic scale
plot(x = sp500.df$Date,
     y = sp500.df$Close,
     type = "l",
     xlab = "Date",
     ylab = "Close Value",
     log = "y",
     main = "S&P 500 Close Values Since 2010(Logarithmic Scale)"
)
```
```{r}
#Plot Close price density overlaid with the normal distribution
ggplot(sp500.df, aes(x=sp500.df$Close)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "pink") + stat_function(fun = dnorm, lwd = 2, col = 'blue', args = list(mean = mean(sp500.df$Close), sd = sd(sp500.df$Close)))
```


```{r}
# Plot the Trading Volume on a logarithmic scale
plot(x = sp500.df$Date,
     y = sp500.df$Volume,
     type = "l",
     xlab = "Date",
     ylab = "Volume",
     log = "y",
     main = "S&P 500 Volumes Traded Since 2010(Logarithmic Scale)"
)
```
```{r}
#Plot Volume density overlaid with the normal distribution
ggplot(sp500.df, aes(x=sp500.df$Volume)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "pink") + stat_function(fun = dnorm, lwd = 2, col = 'blue', args = list(mean = mean(sp500.df$Volume), sd = sd(sp500.df$Volume)))
```


```{r}
# Plot the close Adjusted prices on a logarithmic scale
plot(x = sp500.df$Date,
     y = sp500.df$High,
     type = "l",
     xlab = "Date",
     ylab = "Close Adjusted Value",
     log = "y",
     main = "S&P 500 Close Adjusted Values Since 2010(Logarithmic Scale)"
)
```
```{r}
#Plot Close Adjusted price density overlaid with the normal distribution
ggplot(sp500.df, aes(x=sp500.df$Adjusted)) + geom_histogram(bins = 50, aes(y = ..density..), col = "red", fill = "pink") + stat_function(fun = dnorm, lwd = 2, col = 'blue', args = list(mean = mean(sp500.df$Adjusted), sd = sd(sp500.df$Adjusted)))
```






```{r}
#Duplicate GSPC data on logarithmic scale
GSPC.log <- log(GSPC)
head(GSPC.log)
```

The return from a price change can be viewed as either a discrete return or as a continuous logarithmic return.  The continuous logarithmic return is favoured in finance as it describes continuously compounded returns (Feuct, 2018).  The other reason for using the logarithmic scale for calculating returns is that the discrete return can never have the desired property of following a Gaussian normal distribution.  If we use the log continuous returns we can demonstrate that the data approximates the normal distribution. 

```{r}
# Continuous Adjusted Close Return
GSPC$Con_daily_return <- diff.xts(log(GSPC$Adjusted))
```

```{r}
#Check head of new xts.object
head(GSPC)
nrow(GSPC)
```


```{r}
# Remove NAs created by calcualtion of daily return
GSPC <- na.exclude(GSPC)
```

```{r}
# Recheck head 
head(GSPC)
```

```{r}
# Plot the continuous daily returns on a logarithmic scale
plot(x = index(GSPC),
     y = GSPC$Con_daily_return,
     type = "l",
     xlab = "Date",
     ylab = "Continuous Daily Returns",
     main = "S&P 500 Continuous Daily Returns Since 2010(Logarithmic Scale)"
)
```
From the above plot we can see the that logarithmic returns have a constant mean, variance, and standard deviation and therefore are stationary and can be used for analysis.

```{r}
#Boxplot Continuous Daily Returns to look for outliers
library("PerformanceAnalytics")
chart.Boxplot(GSPC$Con_daily_return)
```

The boxplot is negatively skewed with a considerable number of preponderance of outliers and one extreme value on the left.  These will need further investigation.

```{r}
#Plot histogram of density
chart.Histogram(GSPC$Con_daily_return[,1,drop=F], main = "Density", breaks=50, methods = c("add.density", "add.normal"))
```


```{r}
#Plot skew and kurtosis
chart.Histogram(GSPC$Con_daily_return[,1,drop=F], main = "Skew and Kurt", methods = c("add.centered", "add.rug"))
```

The boxplot identified a number of outliers in the current data.  The histogram of density with the normal distribution overlaid and the density confirm what was noted earlier about the approximation of the normal distribution with a preponderance of scores around the mean and longer tails.  The skew and kurtosis plot show no skew and and confirm a leptokuric distribution.  This means there is a preponderance of scores around the mean and that is caused by occasional extreme outliers.  This noisy distribution is part of what makes predicting the stock market such a challenge and keeps people investing/trading. The large occassional market move that cause the outliers is an integral part of the puzzle for stock market prediction.  Replacing some of the outliers would be an option but removing them would not make sense due the relation of time-series data.  For these reasons it has been decided to move forward with the remainder of the analysis without treating outliers at the moment. 


## DERIVED DATA ##

In 2003, Kim used 12 technical indicators to train his Support Vector Machine (SVM) to predict stock price movement.  The www.stockcharts.com website details 55 different Overlays and Technical Indicators that investors can use to make their predictions.    The TTR package in R provides tools to calculate up to 42 technical indicators from stock data.  The remainder of this section will calculate the relevant indicators for the current data, default values will be used throughout.  

```{r}
# Create copy of GSPC with logarithamic values for Open, High, Low, Close, Volume, Adjusted variables. 
GSPC.log <- subset(GSPC, select = c("Open", "High", "Low", "Close", "Volume", "Adjusted"))
head(GSPC.log, n = 10)
GSPC.log <- log(GSPC.log)

#Add continuous daily returns to GSPC.log
GSPC.log$Con_daily_return <- GSPC$Con_daily_return
```

## STATIONARITY TESTING ##

When perfroming the the ARIMA earlier the Adjusted Close price was tested for stationarity before hand.  Prior calculating the Technical indicators we will test for stationarity in the remaing variables (Open, High, Low, Close, Volume).  Con_daily_return does not need to be checked as it has all ready been differenced and plotted and shown to have a constant mean, variance and standard deviation. 


#Test for serial correlation on OPEN Values
```{r}
#Perform autocorrelation on Open values
acf(GSPC.log$Open, lag.max = 100)
pacf(GSPC.log$Open, lag.max = 100)
```


```{r}
#Run Agumented Dickey Fuller Test
adf.test(GSPC.log$Open)
```

The Augmented Dickey-Fuller test has is -3.38 which is less negative than the tabulated critical value for a sample of greater than 500 at the 95% confidence interval of -3.41 with trend which means we cannot reject the null hypothesis of non-stationaity.  To confirm stationarity we can take the differenced time series and run the Augmented Dickey-Fuller test again.

```{r}
#Difference the data.
diff.open <- diff(GSPC.log$Open, na.pad = F)

# Run Augmented Dickey-Fuller Test again
adf.test(diff.open)
```
Now the Augmented Dickey-Fuller statistic is -14.232 which is more negative than either of the comparison statistics and therefore the null hypothesis of non-stationarity can be rejected. 

#Test for serial correlation on High values
```{r}
#Perform autocorrelation on High values
acf(GSPC.log$High, lag.max = 100)
pacf(GSPC.log$High, lag.max = 100)
```


```{r}
#Run Agumented Dickey Fuller Test
adf.test(GSPC.log$High)
```

The Augmented Dickey-Fuller test has is -3.202 which is less negative than the tabulated critical values for a sample of greater than 500 at the 95% confidence interval of -3.41 with trend which means we cannot reject the null hypothesis of non-stationaity.  To confirm stationarity we can take the differenced time series and run the Augmented Dickey-Fuller test again.

```{r}
#Difference the data.
diff.high <- diff(GSPC.log$High, na.pad = F)

# Run Augmented Dickey-Fuller Test again
adf.test(diff.high)
```
Now the Augmented Dickey-Fuller statistic is -13.56 which is more negative than either of the comparison statistics and therefore the null hypothesis of non-stationarity can be rejected. 

#Test for serial correlation on Low values
```{r}
#Perform autocorrelation on Low values
acf(GSPC.log$Low, lag.max = 100)
pacf(GSPC.log$Low, lag.max = 100)
```


```{r}
#Run Agumented Dickey Fuller Test
adf.test(GSPC.log$Low)
```

The Augmented Dickey-Fuller test has is -3.4591 which is more negative than the tabulated critical values for a sample of greater than 500 at the 95% confidence interval of -3.41 with trend and -2.86 without trend which means we can reject the null hypothesis of non-stationaity.  

#Test for serial correlation on Close values
```{r}
#Perform autocorrelation on Close values
acf(GSPC.log$Close, lag.max = 100)
pacf(GSPC.log$Close, lag.max = 100)
```


```{r}
#Run Agumented Dickey Fuller Test
adf.test(GSPC.log$Close)
```

The Augmented Dickey-Fuller test has is -3.3552 which is less negative than the tabulated critical values for a sample of greater than 500 at the 95% confidence interval of -3.41 with trend and -2.86 without trend which means we can reject the null hypothesis of non-stationaity.  


#Test for serial correlation on Volume values
```{r}
#Perform autocorrelation on Volume values
acf(GSPC.log$Volume, lag.max = 100)
pacf(GSPC.log$Volume, lag.max = 100)
```


```{r}
#Run Agumented Dickey Fuller Test
adf.test(GSPC.log$Volume)
```

The Augmented Dickey-Fuller test has is -8.02 which is more negative than the tabulated critical values for a sample greater than 500 at the 95% confidence interval of -3.41 with trend and -2.86 without trend which means we can reject the null hypothesis of non-stationaity.  

## CALCULATE TECHNICAL INDICATORS ##

# 1.  Calculate Split and dividend adjusted ratios - not necessary as quantmod/yahoo provide adjusted close
# values


```{r}
# 2.  Calculate Welles Wilder's Directional Movement Index
wwdmi <- ADX(HLC(GSPC.log))
summary(wwdmi)
head(wwdmi)
class(wwdmi)

# create xts object with complette cases
wwdmi2 <- na.exclude(wwdmi)

#Run Agumented Dickey Fuller Test
adf.test(wwdmi2$DIp)
adf.test(wwdmi2$DIn)
adf.test(wwdmi2$DX)
adf.test(wwdmi2$ADX)
```

```{r}
# 3.  Calculate Aroon
aroon20 <- aroon(c(GSPC.log$High, GSPC.log$Low), n = 20)
summary(aroon20)

aroon20.2 <- na.exclude(aroon20)
adf.test(aroon20.2$aroonUp)
adf.test(aroon20.2$aroonDn)
adf.test(aroon20.2$oscillator)
```


```{r}
# 4. Calculate True Range/Average True Range
atr14 <- ATR(HLC(GSPC.log))
summary(atr14)

#Perform Dickey-Fuller Test
atr14.2 <- na.exclude(atr14)
adf.test(atr14.2$tr)
adf.test(atr14.2$atr)
adf.test(atr14.2$trueHigh)
adf.test(atr14.2$trueLow)

atr14.3 <- atr14.2

#Difference trueHigh and trueLow
atr14.3$trueHigh <- diff(atr14.3$trueHigh)
atr14.3$trueLow <- diff(atr14.3$trueLow)

#Remove NAs 
atr14.3 <- na.exclude(atr14.3)

#Perform Dickey-Fuller Test
adf.test(atr14.3$trueHigh)
adf.test(atr14.3$trueLow)
#atr14.3 to be used in analysis
```

```{r}
# 5. Calculate Bollinger Bands High, Low, Close
bbands20 <- BBands(HLC(GSPC.log))
summary(bbands20)

#Perform Dickey-Fuller Test
bbands20.2 <- na.exclude(bbands20)
adf.test(bbands20.2$dn)
adf.test(bbands20.2$mavg)
adf.test(bbands20.2$up)
adf.test(bbands20.2$pctB)

bbands20.3 <- bbands20.2

#Difference variables showing autocorrelation
bbands20.3$dn <- lag(diff(bbands20.3$dn), -1)
bbands20.3$mavg <- lag(diff(bbands20.3$mavg), -1)
bbands20.3$up <- lag(diff(bbands20.3$up), -1)

#Perform Dickey-Fuller Test
bbands20.3 <- na.exclude(bbands20.3)
adf.test(bbands20.3$dn)
adf.test(bbands20.3$mavg)
adf.test(bbands20.3$up)
```




```{r}
# 6. Calculate Commodity Channel Index(CCI)
cci20 <- CCI(HLC(GSPC.log))
summary(cci20)

cci20.2 <- na.exclude(cci20)

adf.test(cci20.2$cci)
```


```{r}
# 7. Calculate Chaikin Accumuluation / Distribution
chaikin_ad <- chaikinAD(HLC(GSPC.log), GSPC.log$Volume)
summary(chaikin_ad)

#Perform Dickey-Fuller Test
chaikin_ad.2 <- na.exclude(chaikin_ad)
adf.test(chaikin_ad.2)

#Difference variable as it shows autocorrelation
chaikin_ad.3 <- chaikin_ad.2
chaikin_ad.3 <- diff(chaikin_ad.3)

#Perform Dickey-Fuller Test
chaikin_ad.3 <- na.exclude(chaikin_ad.3)
adf.test(chaikin_ad.3)
#chaikin_ad.2 to be used in Analysis
```

```{r}
# 8.  Calculate Chainkin Volatility
chaikin_vol <- chaikinVolatility(HLC(GSPC.log))
summary(chaikin_vol)

#Perform Dickey-Fuller Test
chaikin_vol.2 <- na.exclude(chaikin_vol)
adf.test(chaikin_vol.2$EMA)
```

```{r}
# 9. Calculate Close Location Value
close_lv <- CLV(HLC(GSPC.log))
summary(close_lv)

#Perform Dickey-Fuller test
close_lv.2 <- na.exclude(close_lv)
adf.test(close_lv.2)
```

```{r}
# 10. Calculate Chaikin Money Flow
chaikin_mf <- CMF(HLC(GSPC.log), GSPC.log$Volume)
summary(chaikin_mf)

#Perform Dickey-Fuller Test
chaikin_mf.2 <- na.exclude(chaikin_mf)
adf.test(chaikin_mf.2)
```

```{r}
# 11. Calculate Chande Momentum Oscillator
cmo <- CMO(GSPC.log$Close)
summary(cmo)

#Perform Dickey-Fuller teset
cmo.2 <- na.exclude(cmo)
adf.test(cmo.2)
```

```{r}
# 12. Calculate Donchian Channel
dc <- DonchianChannel(GSPC.log$High, GSPC.log$Low)
summary(dc)

#Perfrom Dickey-Fuller Test
dc.2 <- na.exclude(dc)
adf.test(dc.2$high)
adf.test(dc.2$mid)
adf.test(dc.2$low)

#Difference variables showing autocorrelation
dc.3 <- dc.2
dc.3$high <- diff(dc.3$high)
dc.3$mid <- diff(dc.3$mid)
dc.3$low <- diff(dc.3$low)

#Perform Dickey-Fuller Test
dc.3 <- na.exclude(dc.3)
adf.test(dc.3$high)
adf.test(dc.3$mid)
adf.test(dc.3$low)
#dc.3 to be used in analysis
```

```{r}
# 13. Calculate Price De-Trended Price Oscillator
price_dpo <- DPO(GSPC.log$Close)
summary(price_dpo)

#Perform Dickey-Fuller Test
price_dpo.2 <- na.exclude(price_dpo)
adf.test(price_dpo.2$Close)
```

```{r}
# 14. Calculate Volume De-Trended Price Oscillator
volume_dpo <- DPO(GSPC.log$Volume)
summary(volume_dpo)

volume_dpo.2 <- na.exclude(volume_dpo)
adf.test(volume_dpo.2$Volume)
```

```{r}
# 15.  Calculate DV Intermediate Oscillator
dvi <- DVI(GSPC.log$Close)
summary(dvi)

#Perform Dickey-Fuller Test
dvi.2 <- na.exclude(dvi)
adf.test(dvi.2$dvi.mag)
adf.test(dvi.2$dvi.str)
adf.test(dvi.2$dvi)
```


```{r}
# 16. Calculate Arms' Ease of Movement Value
emv <- EMV(HLC(GSPC.log), GSPC.log$Volume)
summary(emv)

#Perfrom Dickey-Fuller Test
emv.2 <- na.exclude(emv)
adf.test(emv.2$emv)
adf.test(emv.2$maEMV)
```


```{r}
# 17. Calculate Guppy Mul]tiple Moving Averages
gmma <- GMMA(GSPC.log$Close)
summary(gmma)

#Perfrom Dickey-Fuller Test
gmma.2 <- na.exclude(gmma)
adf.test(gmma.2$`short lag 3`)
adf.test(gmma.2$`short lag 5`)
adf.test(gmma.2$`short lag 8`)
adf.test(gmma.2$`short lag 10`)
adf.test(gmma.2$`short lag 12`)
adf.test(gmma.2$`short lag 15`)
adf.test(gmma.2$`long lag 30`)
adf.test(gmma.2$`long lag 35`)
adf.test(gmma.2$`long lag 40`)
adf.test(gmma.2$`long lag 45`)
adf.test(gmma.2$`long lag 50`)
adf.test(gmma.2$`long lag 60`)

#Difference variables showing serial correlation
gmma.3 <- gmma.2
gmma.3$`short lag 3` <- diff(gmma.3$`short lag 3`)
gmma.3$`short lag 5` <- diff(gmma.3$`short lag 5`)
gmma.3$`short lag 8` <- diff(gmma.3$`short lag 8`)
gmma.3$`short lag 10` <- diff(gmma.3$`short lag 10`)
gmma.3$`short lag 12` <- diff(gmma.3$`short lag 12`)
gmma.3$`short lag 15` <- diff(gmma.3$`short lag 15`)
gmma.3$`long lag 30` <- diff(gmma.3$`long lag 30`)
gmma.3$`long lag 35` <- diff(gmma.3$`long lag 35`)
gmma.3$`long lag 40` <- diff(gmma.3$`long lag 40`)
gmma.3$`long lag 45` <- diff(gmma.3$`long lag 45`)
gmma.3$`long lag 50` <- diff(gmma.3$`long lag 50`)
gmma.3$`long lag 60` <- diff(gmma.3$`long lag 60`)

#Perform Dickey-Fuller Test
gmma.3 <- na.exclude(gmma.3)
adf.test(gmma.3$`short lag 3`)
adf.test(gmma.3$`short lag 5`)
adf.test(gmma.3$`short lag 8`)
adf.test(gmma.3$`short lag 10`)
adf.test(gmma.3$`short lag 12`)
adf.test(gmma.3$`short lag 15`)
adf.test(gmma.3$`long lag 30`)
adf.test(gmma.3$`long lag 35`)
adf.test(gmma.3$`long lag 40`)
adf.test(gmma.3$`long lag 45`)
adf.test(gmma.3$`long lag 50`)
adf.test(gmma.3$`long lag 60`)
#gmma.3 to be used in analysis
```


```{r}
# 18. Calculate Know Sure Thing
kst <- KST(GSPC.log$Close)
summary(kst)

#Perform Dickey-Fuller Test
kst.2 <- na.exclude(kst)
adf.test(kst.2$kst)
adf.test(kst.2$signal)
```


```{r}
# 19. Calculate Know Sure Thing with 4 Moving Averages
kst4ma <- KST(GSPC.log$Close,
              maType = list(list(SMA), list(EMA), list(DEMA), list(WMA)))
summary(kst4ma)

#Perform Dickey-Fuller Test
kst4ma.2 <- na.exclude(kst4ma)
adf.test(kst4ma.2$kst)
adf.test(kst4ma.2$signal)
```


```{r}
# 20. Calculate MACD Oscillator
macd <- MACD(GSPC.log$Close, 12, 26, 9, maType = "EMA")
summary(macd)

#Perform Dickey-Fuller Test
macd.2 <- na.exclude(macd)
adf.test(macd.2$macd)
adf.test(macd.2$signal)
```


```{r}
# 21. Calculate MACD Oscillator with 3 Moving Averages
macd2 <- MACD(GSPC.log$Close, 12, 26, 9,
              maType = list(list(SMA), list(EMA, wilder = TRUE), list(SMA)))
summary(macd2)

#Perform Dickey-Fuller Test
macd2.2 <- na.exclude(macd2)
adf.test(macd2.2$macd)
adf.test(macd2.2$signal)
```


```{r}
# 22. Calculate Money Flow Index
mfi <- MFI(HLC(GSPC.log), GSPC.log$Volume)
summary(mfi)

#Perfrom Dickey-Fuller Test
mfi.2 <- na.exclude(mfi)
adf.test(mfi.2$mfi)
```

```{r}
# 23. Calculate On Balance Volume
obv <- OBV(GSPC.log$Close, GSPC.log$Volume)
summary(obv)

#Perfrom Dickey-Fuller Test
obv.2 <- na.exclude(obv)
adf.test(obv.2$obv)

#Difference as it is showing serial correlation
obv.3 <- obv.2
obv.3$obv <- diff(obv.3$obv)
obv.3 <- na.exclude(obv.3)

#Perform Dickey-Fuller Test
adf.test(obv.3$obv)
#obv.3 to be used in analysis
```


```{r}
# 24. Calcualte Volatility Price Bands
pbands <- PBands(GSPC.log$Close)
summary(pbands)

#Perform Dickey-Fuller Test
pbands.2 <- na.exclude(pbands)
adf.test(pbands.2$dn)
adf.test(pbands.2$center)
adf.test(pbands.2$up)         

#Difference variables showing autocorrelation
pbands.3 <- pbands.2
pbands.3$dn <- diff(pbands.3$dn)
pbands.3$center <- diff(pbands.3$center)
pbands.3$up <- diff(pbands.3$up)

#Perform Dickey-Fuller Test
pbands.3 <- na.exclude(pbands.3)
adf.test(pbands.3$dn)
adf.test(pbands.3$center)
adf.test(pbands.3$up)
#pbands.3 to be used in analysis
```


```{r}
# 25. Calculate Rate of Change
roc <- ROC(GSPC.log$Close)
summary(roc)

#Perform Dickey-Fuller Test
roc.2 <- na.exclude(roc)
adf.test(roc.2$Close)
```


```{r}
# 26. Calculate Momentum
mom <- momentum(GSPC.log$Close)
summary(mom)

#Perform Dickey-Fuller Test
mom.2 <- na.exclude(mom)
adf.test(mom.2$Close)
```


```{r}
# 27. Calculate RSI
rsi <- RSI(GSPC.log$Close)
summary(rsi)

#Perfrom Dickey-Fuller Test
rsi.2 <- na.exclude(rsi)
adf.test(rsi.2$rsi)
```


```{r}
# 28. Calculate RSI of one Moving Average Type for both Moving Averages
rsima1 <- RSI(GSPC.log$Close, n = 14, maType = "WMA", wts = GSPC.log$Volume)
summary(rsima1)

#Perform Dickey-Fuller Test
rsima1.2 <- na.exclude(rsima1)
adf.test(rsima1.2$rsi)
```


```{r}
# 29.  Calculate RSI of two different Moving averages for both moving averages
rsima2 <- RSI(GSPC.log$Close, n = 14, maType = list(maUp = list(EMA, ratio = 1/5),
                                                     maDown = list(WMA, wts = 1:10)))
summary(rsima2)

#Perform Dickey-Fuller Test
rsima2.2 <- na.exclude(rsima2)
adf.test(rsima2.2)
```


```{r}
# 30. Calculate Percent Rank over a Moving Window
percent_rank <- runPercentRank(GSPC.log$Close, n = 125, cumulative = FALSE, exact.multiplier = 0.5)
summary(percent_rank)

#Perform Dickey-Fuller Test
percent_rank.2 <- na.exclude(percent_rank)
adf.test(percent_rank.2)
```


```{r}
# 31. Calculate Sum over a 10 day rolling window
runsum10 <- runSum(GSPC.log$Close)
summary(runsum10)

# Perform Dickey-Fuller Test
runsum10.2 <- na.exclude(runsum10)
adf.test(runsum10.2)

#Difference as showing signs of autocorrelation
runsum10.3 <- runsum10.2
runsum10.3 <- diff(runsum10.3)

#Perform Dickey_Fuller Test
runsum10.3 <- na.exclude(runsum10.3)
adf.test(runsum10.3)
#runsum10.3 to be used in analysis
```


```{r}
# 32. Calculate Minimun over a 10 day rolling window
runmin10 <- runMin(GSPC.log$Close)
summary(runmin10)

#Perform Dickey-Fuller Test
runmin10.2 <- na.exclude(runmin10)
adf.test(runmin10.2)

#Difference due to autocorrelation
runmin10.3 <- runmin10.2
runmin10.3 <- diff(runmin10.3)

#Perform Dickey-Fuller Test
runmin10.3 <- na.exclude(runmin10.3)
adf.test(runmin10.3)
```


```{r}
# 33. Calculate Maximum over a 10 day rolling window
runmax10 <- runMax(GSPC.log$Close)
summary(runmax10)

# Perform Dickey-Fuller Test
runmax10.2 <- na.exclude(runmax10)
adf.test(runmax10.2)

#Difference due to autocorrelation
runmax10.3 <- runmax10.2
runmax10.3 <- diff(runmax10.3)

#Perform Dickey-Fuller Test
runmax10.3 <- na.exclude(runmax10.3)
adf.test(runmax10.3)
#runmax10.3 to be used in analysis
```


```{r}
# 34. Calculate Mean over a 10 day rolling window
runmean10 <- runMean(GSPC.log$Close)
summary(runmean10)

#Perform Dickey_Fuller TEst
runmean10.2 <- na.exclude(runmean10)
adf.test(runmean10.2)

#Difference due to autocorrelation
runmean10.3 <- runmean10.2
runmean10.3 <- diff(runmean10.3)

#Perform Dickey-Fuller Test
runmean10.3 <- na.exclude(runmean10.3)
adf.test(runmean10.3)
#runmean10.3 to be used in analysis
```


```{r}
#35. Calculate Median over a 10 day rolling window
runmedian10 <- runMedian(GSPC.log$Close)
summary(runmedian10)

# Perform Dickey-Fuller Test
runmedian10.2 <- na.exclude(runmedian10)
adf.test(runmedian10.2)

#Difference due to serial correlation
runmedian10.3 <- runmedian10.2
runmedian10.3 <- diff(runmedian10.3)

#Perform Dickey-Fuller Test
runmedian10.3 <- na.exclude(runmedian10.3)
adf.test(runmedian10.3)
#runmedian10.3 to be used in analysis
```


```{r}
#36. Calculate Standard Deviation over a 10 day rolling window
runsd10 <- runSD(GSPC.log$Close) 
summary(runsd10)

#Perform Dickey-Fuller Test
runsd10.2 <- na.exclude(runsd10)
adf.test(runsd10.2)
```


```{r}
#37. Calculate mean/median deviations over a 10 day rolling window
runmad10 <- runMAD(GSPC.log$Close)
summary(runmad10)

#Perform Dickey_Fuller Test
runmad10.2 <- na.exclude(runmad10)
adf.test(runmad10.2)
```


```{r}
#38. Calcualte weight sum over a 10 day rolling window
wildersum10 <- wilderSum(GSPC.log$Close)
summary(wildersum10)

wildersum10.2 <- na.exclude(wildersum10)
adf.test(wildersum10.2)

#Difference due to autocorrelation
wildersum10.3 <- wildersum10.2
wildersum10.3 <- diff(wildersum10.3)

#Perform Dickey_Fuller Test
wildersum10.3 <- na.exclude(wildersum10.3)
adf.test(wildersum10.3)
```


```{r}
#39. Calculate Parabolic Stop and Reverse
sar <- SAR(HLC(GSPC.log))
summary(sar)

#Perform Dickey_Fuller Test
sar.2 <- na.exclude(sar)
adf.test(sar.2)

#difference due to autocorrelation
sar.3 <- sar.2
sar.3 <- diff(sar.3)

#Perform Dickey_Fuller test
sar.3 <- na.exclude(sar.3)
adf.test(sar.3)
```


```{r}
# 40. Calculate simple 10 day moving average
sma10 <- SMA(GSPC.log$Close)
summary(sma10)

#Perform Dickey-Fuller Test
sma10.2 <- na.exclude(sma10)
adf.test(sma10.2)

#Difference due to autocorrelation
sma10.3 <- sma10.2
sma10.3 <- diff(sma10.3)

#Perform Dickey-Fuller Test
sma10.3 <- na.exclude(sma10.3)
adf.test(sma10.3)
#sma10.3 to be used in analysis
```


```{r}
# 41. Calculate exponentially weighted 10 day average
ema10 <- EMA(GSPC.log$Close) 
summary(ema10)

#Perform Dickey-Fuller test
ema10.2 <- na.exclude(ema10)
adf.test(ema10.2)

#Difference due to auto-correlation
ema10.3 <- ema10.2
ema10.3 <- diff(ema10.3)

#Perform Dickey-Fuller Test
ema10.3 <- na.exclude(ema10.3)
adf.test(ema10.3)
#ema10.3 to be used in analysis
```


```{r}
# 42. Calcualte double exponential weighted 10 day moving average
dema10 <- DEMA(GSPC.log$Close)
summary(dema10)

# perform dickey-fuller test
dema10.2 <- na.exclude(dema10)
adf.test(dema10.2)

#Difference due to autocorrelation
dema10.3 <- dema10.2
dema10.3 <- diff(dema10.3)

#Perform dickey-fuller test
dema10.3 <- na.exclude(dema10.3)
adf.test(dema10.3)
```


```{r}
# 43. Calculate weighted 10 day moving average
wma10 <- WMA(GSPC.log$Close)
summary(wma10)

#Perform Dickey-Fuller Test
wma10.2 <- na.exclude(wma10)
adf.test(wma10.2)

#Difference due to auto-correlation
wma10.3 <- wma10.2
wma10.3 <- diff(wma10.3)

#Perform Dickey-Fuller Test
wma10.3 <- na.exclude(wma10.3)
adf.test(wma10.3)
#wma10.3 to be used in analysis
```


```{r}
# 44. Calculate elastic, volume weighted 10 day moving average
evwma10 <- EVWMA(GSPC.log$Close, GSPC.log$Volume)
summary(evwma10)

# Perform Dickey-Fuller Test
evwma10.2 <- na.exclude(evwma10)
adf.test(evwma10.2)

#Difference due to serial correlation
evwma10.3 <- evwma10.2
evwma10.3 <- diff(evwma10.3)

#Perform Dickey-Fuller Test
evwma10.3 <- na.exclude(evwma10.3)
adf.test(evwma10.3)
```


```{r}
# 45 Calculate Zero lag exponential 10 day moving average
zlema10 <- ZLEMA(GSPC.log$Close)
summary(zlema10)

# Perform Dickey-Fuller Test
zlema10.2 <- na.exclude(zlema10)
adf.test(zlema10.2)

#Difference due to autocorrelation\
zlema10.3 <- zlema10.2
zlema10.3 <- diff(zlema10.3)

# Perform Dickey-Fuller Test
zlema10.3 <- na.exclude(zlema10.3)
adf.test(zlema10.3)
```


```{r}
# 46. Calculate Volume weighted 10 day average price
vwap10 <- VWAP(GSPC.log$Close, GSPC.log$Volume)
summary(vwap10)

#Perform dickey-fuller test
vwap10.2 <- na.exclude(vwap10)
adf.test(vwap10.2)

#Difference due to autocorrelation
vwap10.3 <- vwap10.2
vwap10.3 <- diff(vwap10.3)

#Perform Dickey-Fuller Test
vwap10.3 <- na.exclude(vwap10.3)
adf.test(vwap10.3)
```


```{r}
# 47. Calculate Hull 20 day moving average
hma20 <- HMA(GSPC.log$Close)
summary(hma20)

# Perform Dickey-Fuller Test
hma20.2 <- na.exclude(hma20)
adf.test(hma20.2)

#Difference due to serial correlation
hma20.3 <- hma20.2
hma20.3 <- diff(hma20.3)

#Perform Dickey-Fuller Test
hma20.3 <- na.exclude(hma20.3)
adf.test(hma20.3)
```


```{r}
# 48. Calculate Arnaud Legoux 9 day moving average
alma9 <- ALMA(GSPC.log$Close)
summary(alma9)

#Perform Dickey-Fuller Test
alma9.2 <- na.exclude(alma9)
adf.test(alma9.2)

#Difference due to autocorrelation
alma9.3 <- alma9.2
alma9.3 <- diff(alma9.2)

#Perform Dickey-Fuller Test
alma9.3 <- na.exclude(alma9.3)
adf.test(alma9.3)
```


```{r}
# 49. Calculate simple 20 day moving average
sma20 <- SMA(GSPC.log$Close, 20)
summary(sma20)

#Perform Dickey-Fuller Test
sma20.2 <- na.exclude(sma20)
adf.test(sma20.2)

#Difference Due to autocorrelation
sma20.3 <- sma20.2
sma20.3 <- diff(sma20.3)

#Perform Dickey-Fuller Test
sma20.3 <- na.exclude(sma20.3)
adf.test(sma20.3)
```


```{r}
# 50. Calculate double expoential 20 day moving average
dema20 <- DEMA(GSPC.log$Close, 20)
summary(dema20)

#Perform dickey-Fuller Test
dema20.2 <- na.exclude(dema20)
adf.test(dema20.2)

#Difference due to autocorrelation
dema20.3 <- dema20.2
dema20.3 <- diff(dema20.3)

#Perform Dickey Fuller Test
dema20.3 <- na.exclude(dema20.3)
adf.test(dema20.3)
```


```{r}
# 51. Calculate elastic, volume weighted 20 day moving average
evwma20 <- EVWMA(GSPC.log$Close, GSPC.log$Volume, 20)
summary(evwma20)

#Perform Dickey-Fuller Test
evwma20.2 <- na.exclude(evwma20)
adf.test(evwma20.2)

#Differenec due to autocorrelation
evwma20.3 <- evwma20.2
evwma20.3 <- diff(evwma20.3)

#Perform Dickey-Fuller Test
evwma20.3 <- na.exclude(evwma20.3)
adf.test(evwma20.3)
```


```{r}
# 52. Calculate Zero lag exponential 20 day moving average 
zlema20 <- ZLEMA(GSPC.log$Close, 20)
summary(zlema20)

#Perform Dickey-Fuller Test
zlema20.2 <- na.exclude(zlema20)
adf.test(zlema20.2)

#Difference due to autocorrelation
zlema20.3 <- zlema20.2
zlema20.3 <- diff(zlema20.3)

#Perform Dickey-Fuller TEst
zlema20.3 <- na.exclude(zlema20.3)
adf.test(zlema20.3)
```


```{r}
# 53. Calculate Signal to Noise Ratio over 10 days
snr10 <- SNR(HLC(GSPC.log), 10)
summary(snr10)

#Perform Dickey_Fuller test
snr10.2 <- na.exclude(snr10)
adf.test(snr10.2)
```


```{r}
# 54. Calculate signal to norise ratio over 20 days
snr20 <- SNR(HLC(GSPC.log), 20)
summary(snr20)

#Perform Dickey-Fuller Test
snr20.2 <- na.exclude(snr20)
adf.test(snr20.2)
```

```{r}
# 55. Calculate Stochastic Oscillators
stoch_osc <- stoch(HLC(GSPC.log))
summary(stoch_osc)

#Perform Dickey-Fuller Test
stoch_osc.2 <- na.exclude(stoch_osc)
adf.test(stoch_osc.2$fastK)
adf.test(stoch_osc.2$fastD)
adf.test(stoch_osc.2$slowD)
```


```{r}
# 56. Calculate Stochastic Momentum Indexes
stoch_smi <- SMI(HLC(GSPC.log))
summary(stoch_smi)

#Perform Dickey-Fuller Test
stoch_smi.2 <- na.exclude(stoch_smi)
adf.test(stoch_smi.2$SMI)
adf.test(stoch_smi.2$signal)
```

```{r}
# 57. Calculate Stochastic WPR 
stoch_wpr <- WPR(HLC(GSPC.log))
summary(stoch_wpr)

#Perform Dickey-Fuller Test
stoch_wpr.2 <- na.exclude(stoch_wpr)
adf.test(stoch_wpr.2)
```


```{r}
# 58. Calculate stochastic 2MA
stoch_2ma <- stoch(HLC(GSPC.log),
                   maType=list(list(SMA), list(EMA, wilder=TRUE), list(SMA)) )
summary(stoch_2ma)

#Perform Dickey-Fuller Test
stoch_2ma.2 <- na.exclude(stoch_2ma)
adf.test(stoch_2ma.2$fastK)
adf.test(stoch_2ma.2$fastD)
adf.test(stoch_2ma.2$slowD)
```


```{r}
# 59. Calculate SMI 3MA
smi_3ma <- SMI(HLC(GSPC.log),
               maType=list(list(SMA), list(EMA, wilder=TRUE), list(SMA)) )
summary(smi_3ma)

#Perform Dickey-Fuller Test
smi_3ma.2 <- na.exclude(smi_3ma)
adf.test(smi_3ma.2$SMI)
adf.test(smi_3ma.2$signal)
```


```{r}
# 60 Calculate stochastic RSI
stoch_rsi <- stoch(RSI(GSPC.log$Close))
summary(stoch_rsi)

#Perform Dickey-Fuller Test
stoch_rsi.2 <- na.exclude(stoch_rsi)
adf.test(stoch_rsi.2$fastK)
adf.test(stoch_rsi.2$fastD)
adf.test(stoch_rsi.2$slowD)
```


```{r}
# 61 Calculate Trend Detection Index 20 days
tdi20 <- TDI(GSPC.log$Close)
summary(tdi20)

#Perform Dickey-Fuller Test
tdi20.2 <- na.exclude(tdi20)
adf.test(tdi20.2$tdi)
adf.test(tdi20.2$di)
```


```{r}
# 62. Calculate Trend Detection Index 30 days
tdi30 <- TDI(GSPC.log$Close, 30)
summary(tdi30)

#Perform Dickey-Fuller Test
tdi30.2 <- na.exclude(tdi30)
adf.test(tdi30.2$tdi)
adf.test(tdi30.2$di)
```


```{r}
# 63. Calculate Triple Smoothed Exponential Oscillator
trix20 <- TRIX(GSPC.log$Close)
summary(trix20)

#Perform Dickey_fuller test
trix20.2 <- na.exclude(trix20)
adf.test(trix20.2$TRIX)
adf.test(trix20.2$signal)
```


```{r}
# 64. Calculate TRIX 4 moving averages
trix_4 <- TRIX(GSPC.log$Close,
               maType=list(list(SMA), list(EMA, wilder=TRUE), list(SMA), list(DEMA)))
summary(trix_4)

#Perform Dickey-Fuller test
trix_4.2 <- na.exclude(trix_4)
adf.test(trix_4.2$TRIX)
adf.test(trix_4.2$signal)
```


```{r}
# 65. Calculate ultimate oscillator
ult_osc <- ultimateOscillator(HLC(GSPC.log))
summary(ult_osc)

#Perform Dickey-Fuller Test
ult_osc.2 <- na.exclude(ult_osc)
adf.test(ult_osc.2)
```


```{r}
# 66. Calculate vertical horizontal filter close
vhf_close <- VHF(GSPC.log$Close)
summary(vhf_close)

#Perform Dickey-fuller test
vhf_close.2 <- na.exclude(vhf_close)
adf.test(vhf_close.2)
```


```{r}
# 67. Calculate vertical horizontal filter High low
vhf_hilo <- VHF(HLC(GSPC.log))
summary(vhf_hilo)

#Perform Dickey-Fuller Test
vhf_hilo.2 <- na.exclude(vhf_hilo)
adf.test(vhf_hilo.2)
```


```{r}
# 68. Calculate close to close volatility
v_close <- volatility(OHLC(GSPC.log), calc = "close")
summary(v_close)

#Perform Dickey-Fuller Test
v_close.2 <- na.exclude(v_close)
adf.test(v_close.2)
```


```{r}
# 69. Calculate close to close with a mean of 0 volatility
v_close0 <- volatility(OHLC(GSPC.log), calc="close", mean0=TRUE)
summary(v_close0)

#Perform Dickey-Fuller Test
v_close0.2 <- na.exclude(v_close0)
adf.test(v_close0.2)
```


```{r}
# 70. Calcualte garman volatility
v_gk <- volatility(OHLC(GSPC.log), calc="garman")
summary(v_gk)

#Perform Dickey-Fuller Test
v_gk.2 <- na.exclude(v_gk)
adf.test(v_gk.2)
```


```{r}
# 71. Calculate parkinson volatility
v_par <- volatility(OHLC(GSPC.log), calc = "parkinson")
summary(v_par)

#Perform Dickey-Fuller Test
v_par.2 <- na.exclude(v_par)
adf.test(v_par.2)
```


```{r}
# 72. Calculate rogers satchell volatility
v_rogsat <- volatility(OHLC(GSPC.log), calc = "rogers.satchell")
summary(v_rogsat)

#Perform Dickey-Fuller Test
v_rogsat.2 <- na.exclude(v_rogsat)
adf.test(v_rogsat.2)
```


```{r}
# 73. Calculate garman klass yang zhang volatility
v_gkyz <- volatility(OHLC(GSPC.log), calc = "gk.yz")
summary(v_gkyz)

#Perform Dickey-Fuller Test
v_gkyz.2 <- na.exclude(v_gkyz)
adf.test(v_gkyz.2)
```


```{r}
# 74. Calculate yang zhang volatility
v_yz <- volatility(OHLC(GSPC.log), calc = "yang.zhang")
summary(v_yz)

#Perform Dickey-Fuller TEst
v_yz.2 <- na.exclude(v_yz)
adf.test(v_yz.2)
```


```{r}
# 75. Calculate Williams Accumulation / Distribution
williams_ad <- williamsAD(HLC(GSPC.log))
summary(williams_ad)

#Perform Dickey-Fuller test
williams_ad.2 <- na.exclude(williams_ad)
adf.test(williams_ad.2)

#Difference due to autocorrelation
williams_ad.3 <- williams_ad.2
williams_ad.3 <- diff(williams_ad.3)

#Perform Dickey-Fuller Test
williams_ad.3 <- na.exclude(williams_ad.3)
adf.test(williams_ad.3)
```


```{r}
# 76. Calculate Williams % R
wpr <- WPR(HLC(GSPC.log))
summary(wpr)

#Perform Dickey-Fuller Test
wpr.2 <- na.exclude(wpr)
adf.test(wpr.2)
```

```{r}
# 77. Calculate Zig Zag 10
zigzag10 <- ZigZag(GSPC.log$High, GSPC.log$Low)
summary(zigzag10)

#Perform Dickey-Fuller Test
zigzag10.2 <- na.exclude(zigzag10)
adf.test(zigzag10.2)

#Difference due to autocorrelation
zigzag10.3 <- zigzag10.2
zigzag10.3 <- diff(zigzag10.3)

#Perform Dickey_Fuller Test
zigzag10.3 <- na.exclude(zigzag10.3)
adf.test(zigzag10.3)

#Difference due to autocorrelation
zigzag10.4 <- zigzag10.3
zigzag10.4 <- diff(zigzag10.4)

#Perform Dickey_Fuller Test
zigzag10.4 <- na.exclude(zigzag10.4)
adf.test(zigzag10.4)
```


```{r}
#78. Calculate Zig Zag 20
zigzag20 <- ZigZag(GSPC.log$High, GSPC.log$Low, 20)
summary(zigzag20)

#Perform Dickey-Fuller TEst
zigzag20.2 <- na.exclude(zigzag20)
adf.test(zigzag20.2)

#difference due to autocorrelation
zigzag20.3 <- zigzag20.2
zigzag20.3 <- diff(zigzag20.3)

#Perform Dickey-Fuller Test
zigzag20.3 <- na.exclude(zigzag20.3)
adf.test(zigzag20.3)

#difference due to autocorrelation
zigzag20.4 <- zigzag20.3
zigzag20.4 <- diff(zigzag20.4)

#Perform Dickey-Fuller Test
zigzag20.4 <- na.exclude(zigzag20.4)
adf.test(zigzag20.4)
```


```{r}
#Combine all data
my_final <- merge(GSPC.log, alma9.3, join = "left")
my_final <- merge(my_final, aroon20, join = "left")
my_final <- merge(my_final, atr14.3, join = "left")
my_final <- merge(my_final, bbands20.3, join = "left")
my_final <- merge(my_final, cci20, join = "left")
my_final <- merge(my_final, chaikin_ad.3, join = "left")
my_final <- merge(my_final, chaikin_mf, join = "left")
my_final <- merge(my_final, chaikin_vol, join = "left")
my_final <- merge(my_final, close_lv, join = "left")
my_final <- merge(my_final, cmo, join = "left")
my_final <- merge(my_final, dc.3, join = "left")
my_final <- merge(my_final, dema10.3, join = "left")
my_final <- merge(my_final, dema20.3, join = "left")
my_final <- merge(my_final, dvi, join = "left")
my_final <- merge(my_final, ema10.3, join = "left")
my_final <- merge(my_final, emv, join = "left")
my_final <- merge(my_final, evwma10.3, join = "left")
my_final <- merge(my_final, evwma20.3, join = "left")
my_final <- merge(my_final, gmma.3, join = "left")
my_final <- merge(my_final, hma20.3, join = "left")
my_final <- merge(my_final, kst, join = "left")
my_final <- merge(my_final, kst4ma, join = "left")
my_final <- merge(my_final, macd, join = "left")
my_final <- merge(my_final, macd2, join = "left")
my_final <- merge(my_final, mfi, join = "left")
my_final <- merge(my_final, mom, join = "left")
my_final <- merge(my_final, obv.3, join = "left")
my_final <- merge(my_final, pbands.3, join = "left")
my_final <- merge(my_final, percent_rank, join = "left")
my_final <- merge(my_final, price_dpo, join = "left")
my_final <- merge(my_final, roc, join = "left")
my_final <- merge(my_final, rsi, join = "left")
my_final <- merge(my_final, rsima1, join = "left")
my_final <- merge(my_final, rsima2, join = "left")
my_final <- merge(my_final, runmad10, join = "left")
my_final <- merge(my_final, runmax10.3, join = "left")
my_final <- merge(my_final, runmean10.3, join = "left")
my_final <- merge(my_final, runmedian10.3, join = "left")
my_final <- merge(my_final, runmin10.3, join = "left")
my_final <- merge(my_final, runsd10, join = "left")
my_final <- merge(my_final, runsum10.3, join = "left")
my_final <- merge(my_final, sar.3, join = "left")
my_final <- merge(my_final, sma10.3, join = "left")
my_final <- merge(my_final, sma20.3, join = "left")
my_final <- merge(my_final, smi_3ma, join = "left")
my_final <- merge(my_final, snr10, join = "left")
my_final <- merge(my_final, snr20, join = "left")
my_final <- merge(my_final, stoch_2ma, join = "left")
my_final <- merge(my_final, stoch_osc, join = "left")
my_final <- merge(my_final, stoch_rsi, join = "left")
my_final <- merge(my_final, stoch_smi, join = "left")
my_final <- merge(my_final, stoch_wpr, join = "left")
my_final <- merge(my_final, tdi20, join = "left")
my_final <- merge(my_final, tdi30, join = "left")
my_final <- merge(my_final, trix_4, join = "left")
my_final <- merge(my_final, trix20, join = "left")
my_final <- merge(my_final, ult_osc, join = "left")
my_final <- merge(my_final, v_close, join = "left")
my_final <- merge(my_final, v_close0, join = "left")
my_final <- merge(my_final, v_gk, join = "left")
my_final <- merge(my_final, v_gkyz, join = "left")
my_final <- merge(my_final, v_par, join = "left")
my_final <- merge(my_final, v_rogsat, join = "left")
my_final <- merge(my_final, v_yz, join = "left")
my_final <- merge(my_final, vhf_close, join = "left")
my_final <- merge(my_final, vhf_hilo, join = "left")
my_final <- merge(my_final, volume_dpo, join = "left")
my_final <- merge(my_final, vwap10.3, join = "left")
my_final <- merge(my_final, wildersum10.3, join = "left")
my_final <- merge(my_final, williams_ad.3, join = "left")
my_final <- merge(my_final, wma10.3, join = "left")
my_final <- merge(my_final, wpr, join = "left")
my_final <- merge(my_final, wwdmi, join = "left")
my_final <- merge(my_final, zigzag10.4, join = "left")
my_final <- merge(my_final, zigzag20.4, join = "left")
my_final <- merge(my_final, zlema10.3, join = "left")
my_final <- merge(my_final, zlema20, join = "left")
```

```{r}
#Review data
head(my_final)
tail(my_final)
str(my_final)
summary(my_final)
dim(my_final)
length(my_final)
sum(is.na(my_final))
```


```{r}
## Reduce data from January 1, 2014 to present. 
fd1 <- my_final[index(my_final) >= "2014-01-01"]
fd1 <- fd1[index(fd1) <= "2019-03-30"]
```


```{r}
#inspect data
head(fd1)
summary(fd1)
dim(fd1)
```


```{r}
# find NAs
sum(is.na(fd1))
tail(fd1, n = 130)
```

zigzag10 and zigzag20 have 128 missing values each at the bottom because of the way they are calculated.  These values could be imputed by a number of methods (KNN, Replace with Mean, Forward Propagation).  On this occassion because the number of missing data points is so small and they are at the bottom of the object so their removal will not cause any disruption to the time-series

```{r}
# Remove NAs
fd1 <- na.omit(fd1)

# Count number of rows and columns in final data
dim(fd1)
```


## Correlation ## 

```{r}
#convert to data.frame
library("zoo")
train.df <- fortify.zoo(fd1)
```

```{r}
#check class
class(train.df)
```


```{r}
#review structure
head(train.df)
str(train.df)
```


```{r}
#First make binary dependent variable
price <- train.df$Close - train.df$Open
movement <- ifelse(price > 0, "UP", "DOWN")
movement <- factor(movement)
class(movement)

#add to dataframe
train.df$movement <- movement
class(train.df$movement)

#create data.frame of index and Con_daily return
Daily_return <- train.df[c("Index", "Con_daily_return")] 

#Remove Con_dail_return from train.df
train.df$Con_daily_return <- NULL

head(train.df)
ncol(train.df)
# Make movement the 1st variable in train set
train.df <- train.df[,c(130, 1:129)]

head(train.df)
```


```{r}
#create new data_frame with all variables but the index
my_cor_data <- train.df[c(-2)]
```

```{r}
#inspect correlation data.frame
head(my_cor_data)
```

```{r}
colnames(my_cor_data)
ncol(my_cor_data)
```


```{r}
# Produce correlation matrix 
cor_matrix <- cor(my_cor_data[, c(2:129)])

# Print correlation matrix
print(cor_matrix)
```


```{r}
#Load useful packages
library("corrplot")
# Plot the correlation matrix
corrplot(cor_matrix)
```
Too many correlations to visualize or check manually. 


```{r}
#Find correlations above .8
head(cor_matrix)
hc <- findCorrelation(cor_matrix, cutoff = 0.8)
hc <- sort(hc)
```


```{r}
#Inspect columns to remove
cols_to_remove <- cor_matrix[, c(hc)]
ncol(cols_to_remove)
colnames(cols_to_remove)
```

```{r}
#Create copy of my_data_frame
my_df1 <- train.df
head(my_df1)
```


```{r}
#Removed that are too highly correlated
my_df1$Index <- NULL
my_df1$Open <- NULL
my_df1$High <- NULL
my_df1$Low <- NULL
my_df1$Close <- NULL
my_df1$Adjusted <- NULL
my_df1$Close.1 <- NULL
my_df1$oscillator <- NULL
my_df1$mavg <- NULL
my_df1$pctB <- NULL
my_df1$cci <- NULL
my_df1$chaikin_ad.3<- NULL
my_df1$cmo <- NULL
my_df1$mid <- NULL
my_df1$DEMA <- NULL
my_df1$DEMA.1 <- NULL
my_df1$dvi.mag <- NULL
my_df1$dvi <- NULL
my_df1$EMA.1 <- NULL
my_df1$emv <- NULL
my_df1$evwma10.3 <- NULL
my_df1$evwma20.3 <- NULL
my_df1$short.lag.3 <- NULL
my_df1$short.lag.5 <- NULL
my_df1$short.lag.8 <- NULL
my_df1$short.lag.10 <- NULL
my_df1$short.lag.12 <- NULL
my_df1$short.lag.15 <- NULL
my_df1$long.lag.30 <- NULL
my_df1$long.lag.35 <- NULL
my_df1$long.lag.40 <- NULL
my_df1$long.lag.45 <- NULL
my_df1$long.lag.50 <- NULL
my_df1$long.lag.60 <- NULL
my_df1$hma20.3 <- NULL
my_df1$kst <- NULL
my_df1$signal <- NULL
my_df1$kst.1 <- NULL
my_df1$signal.1 <- NULL
my_df1$macd <- NULL
my_df1$signal.2 <- NULL
my_df1$macd.1 <- NULL
my_df1$signal.3 <- NULL
my_df1$Close.2 <- NULL
my_df1$center <- NULL
my_df1$Close.4 <- NULL
my_df1$rsi <- NULL
my_df1$rsi.1 <- NULL
my_df1$rsi.2 <- NULL
my_df1$runmax10.3 <- NULL
my_df1$runmean10.3 <- NULL
my_df1$runmedian10.3 <- NULL
my_df1$runsd10 <- NULL
my_df1$runsum10.3 <- NULL
my_df1$SMA <- NULL
my_df1$SMA.1 <- NULL
my_df1$SMI <- NULL
my_df1$signal.4 <- NULL
my_df1$fastK <- NULL
my_df1$fastD <- NULL
my_df1$slowD <- NULL
my_df1$fastK.1 <- NULL
my_df1$fastD.1 <- NULL
my_df1$slowD.1 <- NULL
my_df1$fastD.2 <- NULL
my_df1$SMI.1 <- NULL
my_df1$signal.5 <- NULL
my_df1$Close.7 <- NULL
my_df1$di <- NULL
my_df1$di.1 <- NULL
my_df1$TRIX <- NULL
my_df1$TRIX.1 <- NULL
my_df1$signal.7 <- NULL
my_df1$v_close <- NULL
my_df1$v_close0 <- NULL
my_df1$v_gk <- NULL
my_df1$v_gkyz <- NULL
my_df1$v_par <- NULL
my_df1$v_rogsat <- NULL
my_df1$v_yz <- NULL
my_df1$vhf_hilo <- NULL
my_df1$VWAP <- NULL
my_df1$wma10.3 <- NULL
my_df1$Close.9 <- NULL
my_df1$zigzag10.4 <-NULL
my_df1$zlema10.3 <- NULL
my_df1$zlema20 <- NULL
```


## Filter Feature Selection ##


```{r}
library("FSelector")
head(my_df1)
set.seed(123)
weights <- random.forest.importance(movement ~ ., my_df1, importance.type = 1)
print(weights)

#select top 20 predictors
filter1 <- cutoff.k(weights, 20)
print(filter1)
```


```{r}
#create data frame using selected features
filter1.df <- train[c("movement", "clv", "williams_ad.3", "obv", "fastK.2", "trueLow", "trueHigh", "percent_rank", "Close.8", "runmin10.3", "tr", "sar", "high", "EMA", "maEMV", "atr", "dvi.str", "slowD.2",  "Close.3", "DIp", "dn.1")]

head(filter1.df)
dim(filter1.df)
```


```{r}
#10-fold cross validation method used
library("caret")
trainFilter1 <- trainControl(method = "cv", number = 10)
```

## Train different algorithims ##

#K-Nearest Neighbours (knn)
```{r}
fit.knn.filter <- train(movement ~. , data = filter1.df, method = "knn",
                 metric = "Accuracy", preProcess = c("range"), trControl = trainFilter1)
```

#Classification & Regression Trees (CART)
```{r}
fit.cart.filter <- train(movement ~ . , data = filter1.df, method = "rpart", 
                  metric = "Accuracy", preProcess = c("range"), trControl = trainFilter1)
```

#Naive Bayes (NB)
```{r}
fit.nb.filter <- train(movement ~ . , data = filter1.df, method = "nb", 
                  metric = "Accuracy", preProcess = c("range"), trControl = trainFilter1)
```

#SVM with Radial Basis Function (svm)
```{r}
fit.svm.filter <- train(movement ~ . , data = filter1.df, method = "svmRadial", 
                  metric = "Accuracy", preProcess = c("range"), trControl = trainFilter1)
```

#evaluate algorithims using accuracy metric
```{r}
set.seed(5)
results.filter <- resamples(list(KNN=fit.knn.filter, CART=fit.cart.filter, NB=fit.nb.filter, SVM=fit.svm.filter))
summary(results.filter)
dotplot(results.filter)
```

#Wrapper Feature Selection
```{r}
library("mlbench")
library("caret")
myTimeControl <- trainControl(method = "timeslice",
                               initialWindow = 252,
                               horizon = 252,
                               fixedWindow = TRUE)
 
plsFitTime <- train(movement ~.,
                     data = my_df1,
                     method = "pls",
                     preProc = c("center", "scale"),
                     trControl = myTimeControl)
plsFitTime
```

importance <- varImp(model, scale=FALSE)
```{r}
importance <- varImp(plsFitTime, scale=FALSE)
print(importance)
plot(importance)
```

```{r}
#create data frame using selected features - importance above 0.02
wrapper1.df <- my_df1[c("movement", "obv", "clv", "williams_ad.3", "trueLow", "trueHigh", "fastK.2")]

head(wrapper1.df)
dim(wrapper1.df)
```

```{r}
#10-fold cross validation method used
library("caret")
trainWrapper1 <- trainControl(method = "cv", number = 10)
```

## Train different algorithims ##

#K-Nearest Neighbours (knn)
```{r}
fit.knn.wrapper <- train(movement ~. , data = wrapper1.df, method = "knn",
                 metric = "Accuracy", preProcess = c("range"), trControl = trainWrapper1)
```

#Classification & Regression Trees (CART)
```{r}
fit.cart.wrapper <- train(movement ~ . , data = wrapper1.df, method = "rpart", 
                  metric = "Accuracy", preProcess = c("range"), trControl = trainWrapper1)
```

#Naive Bayes (NB)
```{r}
fit.nb.wrapper <- train(movement ~ . , data = wrapper1.df, method = "nb", 
                  metric = "Accuracy", preProcess = c("range"), trControl = trainWrapper1)
```

#SVM with Radial Basis Function (svm)
```{r}
fit.svm.wrapper <- train(movement ~ . , data = wrapper1.df, method = "svmRadial", 
                  metric = "Accuracy", preProcess = c("range"), trControl = trainWrapper1)
```

#evaluate algorithims using accuracy metric
```{r}
results.wrapper <- resamples(list(KNN=fit.knn.wrapper, CART=fit.cart.wrapper, NB=fit.nb.wrapper, SVM=fit.svm.wrapper))
summary(results.wrapper)
dotplot(results.wrapper)
``` 
